\sf Retraction-based first-order feasible methods for difference-of-convex programs with smooth inequality and simple geometric constraints

### 2022-06-15 response_to_referee_v1.tex

%\end{table}

    \item  \textit{\textbf{Reviewer:}} \textit{P26: In table 2, the time of SPGL1 for i = 4 is greater than for i = 6. Does it make any sense?}

	\textbf{Response:} Thanks for this nice point. We double checked and found that the codes are correct. The results in the original Table 2 are the average based on 30 randomly generating instances. When $i = 4$, it seems that two sets of data take exceptionally long time, so it appears that SPGL1 takes more time in the case $i = 4$ than in the case $i = 6$.

In response to the suggestions by the second reviewer, we considered solving compressed sensing problems with measurements in complex numbers in Sections 6.2 and 6.3.2. Section 6.2 has been updated to describe this application, and Table 2 has been updated accordingly. We observe a similar abnormal behavior for SPGL1 that it takes more time in the case $i = 6$ than in the case $i = 8$. % We can also observe that the recovery error of the solution returned by SPGL1 is the largest when $i = 6$.

@@

    \textbf{Response:} Thanks for the comment.

    {\it Difference from [A,B]}: We would like to point out that our method is {\it significantly different} from the one in [A,B]. Indeed, [A,B] employs a cutting plane strategy. In particular, as the algorithm progresses, the number of halfspaces involved in the subproblem {\em grows}, with many of them constructed based on information from the \emph{past iterates}. They exploited the fact that compact convex sets can be written as the intersection of (infinitely many) halfspaces, and deduced convergence based on this {\em without} requiring any descent property of the (interpolated) sequence generated.

    In contrast, our method only requires a {\it fixed} number of halfspaces in each iteration, and the constraint functions are linearized only at the \emph{current iterate}. Thus, the computational effort for solving each subproblem is similar. Moreover, we have to sufficiently regularize the objective of our subproblem so that our retraction (or interpolation) step induces a descent: this is an ingredient not present in the method in [A,B] because their convergence is based on the fact that the intersection of the \emph{growing} number of halfspaces constructed in their algorithm converges to the original feasible set.

    {\it Difference from [42] {  ([46] in this revision)}}: Apart from the retraction step, the key difference is that we are using linear approximations to the constraint functions in the subproblems, while the method in [42] is based on quadratic \emph{majorants} of the constraint functions. Thus, one obtains a feasible point by solving the subproblems in the algorithm in [42], but one does not necessarily obtain a feasible point by solving the subproblem in the FPA method: hence, a retraction step kicks in to restore feasibility. Finally, as mentioned in the first paragraph in page 3, our subproblems based on linear approximations are potentially simpler to solve than those quadratically constrained subproblems in [42].

@@

    {\it Difference from [C,D]:} The algorithms proposed in these papers do not seem to use any approximation to the constraint set or exploit the explicit form of the constraint functions.

    {\it Difference from [E]:} The most closely related algorithm is algorithm 2 in [E]. In this algorithm, the DC constraint function is replaced a convex majorant. In spirit, this is similar to what is done in standard DCA (similar to, for example, [42]), and is different from our algorithm as discussed above. Moreover, the algorithm in [E] constructs subproblems by including only constraints that are approximately ``active". This is an ingredient not considered in our algorithm and it is an interesting future research direction as a possible strategy for constructing simpler subproblems for our algorithm.

    {  Following the suggestions, we have now inserted a paragraph (see the last line in page 2 to line 18 at page 3) in clarifying the relationship with our method with some of the papers suggested.

    Thanks also for the question: whether the convexity assumptions for the constraint functions in the convergence analysis of Algorithm 1 can be established under generalized convexity assumptions (such as quasi-convexity etc). Unfortunately, it seems to us that this is not immediate or trival. The reason lies in the fact that, in our ``retraction step", we make full use of the convexity of the constraint function $g$ to derive the well-definedness of this step (see the argument in two lines before the equation (3.3)). On the other hand, we believe that this would be an interesting future research direction, and we have now discussed this in the conclusion section as one of the future research topics.}

@@

	\item \textit{\textbf{Reviewer:}} \textit{ f) Subproblem (4.6): Should it be $\sigma^x$?}

    \textbf{Response:} Thanks for the comment. It should be $\sigma$ in subproblem (4.6). Indeed, in view of Lemma 4.1(iv), one can see that the inequality constraint in (4.6) is the same as
    \[
    \ell^{x^k}(Ax^k - b) + \langle A^T\nabla \ell^{x^k}(Ax^k - b),x-x^k\rangle \le \tilde \sigma^{x^k}.
    \]

	\item \textit{\textbf{Reviewer:}} \textit{ g) Please compare the algorithms with the method presented in [42], by the third author.}

    \textbf{Response:} Thanks for the comment. The SCP$_{\rm ls}$ was applied in [42] {  ([46] in this revision)} for solving (6.4):
    \begin{equation}\label{pr1}
       \begin{array}{rl}
        \min\limits_{x\in\R^n} & \|x\|_1 - \mu\|x\| \\
        {\rm s.t.} & \|Ax - b\|_{LL_2,\gamma}\leq \overline{\sigma},
       \end{array}
     \end{equation}
    We use the same parameter settings as in [42] for SCP$_{\rm ls}$. The computational results are presented in { Table 2}.

@@

From Table 2, one can see that the recovery errors of the algorithms are comparable, and SCP$_{\rm ls}$ is usually faster. This is likely because SCP$_{\rm ls}$ can take advantage of BB step size (and hence some sort of second-order information), but currently we still do not know how to take advantage of second-order information suitably in our scheme.

From Table 2, it appears that our proposed method is not the method of choice when it comes to solving \eqref{pr1}.
Note that although the subproblems of SCP$_{\rm ls}$ for \eqref{pr1} involve nonlinear constraints, thanks to the polyhedral nature of $\ell_1$ norm, they can still be solved efficiently via some root-finding procedure; see the appendix of [43] { ([47] in this revision)}. This prompts us to consider some other objective functions where the corresponding SCP$_{\rm ls}$ subproblems are not easy while the subproblems for our method (which are linearly constrained) can still be solved efficiently using Newton's method; this setting would be closer to our original motivation, as stated in footnote 1 of the manuscript.

### 2022-06-15 SQP_Retract_rev1.tex
Final version from Guoyin

\section{Introduction}
We consider the following difference-of-convex (DC) optimization problem with smooth inequality and geometric constraints:
\begin{equation}\label{P0}
  \begin{array}{rl}
\min\limits_{x\in\R^n} & P(x) := P_1(x) - P_2(x)\\
{\rm s.t.} & g_i(x)\leq 0,~~ i = 1,\ldots, m,\\
           & x\in C,
  \end{array}
\end{equation}
where $P_1:\R^n\rightarrow\R$ and $P_2:\R^n\rightarrow\R$ are {\color{blue}finite-valued convex} functions, $C\subseteq \R^n$ is a nonempty compact convex set, $g_i:\R^n\rightarrow\R$ is smooth with Lipschitz gradient on $C$ for each $i$, and the feasible set $\mathcal{F} :=\{x\in C:\; g_i(x)\le 0, ~ i = 1,\ldots, m\}$ is nonempty. This model problem covers many important optimization problems arising from diverse areas. For example, one can model the compressed sensing (CS) problem with Cauchy noise by minimizing the difference of $\ell_1$-norm and $\ell_2$-norm \cite{YiLH15} or its variants subject to an inequality constraint defined by the so-called Lorentzian norm \cite{CaBA10}, and the set $C$ in \eqref{P0} can be used for modeling other prior information such as bounds or nonnegativity; more discussions on this particular application can be found in Section~\ref{sec6.2} below. Problem~\eqref{P0} is typically challenging to solve because it is in general nonconvex and nonsmooth.% optimization problem.

In this paper, we are interested in developing first-order feasible methods for solving problem \eqref{P0} that rely on affine approximations to the smooth inequality constraints in the subproblems. Our methods utilize only first-order information, and the subproblems that arise are convex constrained optimization problems with the constraint sets being the intersection of $C$ and a polyhedron.\footnote{On passing, we would like to point out that there are also first-order methods that rely on quadratically approximating the constraint functions (see, for example, \cite{Au13,AuSheTeb10,BoPau16,YuLP20}), which lead to more difficult subproblems.} Moreover, it also has the desirable feature that  all the iterates generated always belong to the feasible region. In the literature, the most widely used method for solving \eqref{P0} when the objective function $P$ is additionally smooth and also involves affine approximations to the constraint set is the so-called sequential quadratic programming (SQP) method: Indeed, this class of methods typically further requires that the objective function $P$ and all the constraint functions $g_i$'s to be twice continuously differentiable. The underlying strategy of SQP methods is to construct an algorithm which, at each iteration, utilizes a convex quadratic programming problem with affine constraints to approximate the original nonlinear optimization problem. The literature is vast and we refer the readers to \cite{Ber95,NoWr06,GiWo12,FlGL02,So09,Au13,BoPau16,WrightTenny04,PaTi93,FlPa08,LawTits01}.
Recent works on SQP-type methods include \cite{Au13,BoPau16}, where the authors proposed and studied the global convergence of some general majorization minimization schemes which cover various SQP-type methods as special cases. However, these SQP-type methods therein are infeasible SQP-type methods, that is, they do not necessarily force all iterates to be feasible. There are also ``feasible SQP methods" that perform arc-search along quadratic curves determined by two directions, namely a descent direction and a feasible direction (see, for example, \cite{PaTi93,FlPa08,LawTits01}). However, these methods make use of the smoothness of the objective and constraint functions to construct the two directions, and it is unclear how their strategies can be adapted to problem~\eqref{P0} that has a possibly nonsmooth objective.

@@

More explicitly, the contributions of this paper are summarized as follows:
\begin{itemize}
  \item We propose a retraction based first-order feasible method that utilizes affine approximations for the constraints in each subproblem for solving problem \eqref{P0} in the case where the constraint functions $g_i$'s are convex under strict feasibility condition, and establish its global subsequential convergence. We also analyze the convergence rate in the fully convex setting, i.e., when $P_2$ is also zero, under suitable Kurdyka-{\L}ojasiewicz (KL) assumptions.
  \item By assuming a ``strong" strict feasibility condition, we then extend our method to solve \eqref{P0} with one single specially structured nonconvex constraint function and establish the global subsequential convergence of the extended method. Our assumptions on the constraint function are general enough to allow the choice of the composition of the Lorentzian norm function with an affine function, a commonly used loss function for compressed sensing problems with Cauchy measurement noise \cite{CaBA10}.
  \item Finally, we examine the KL exponents of several structured optimization models of the form \eqref{P0}, an important quantity which quantifies the convergence rate of the proposed method in the convex setting. Specifically, we show that the extended objective\footnote{This refers to the sum of the objective and the indicator function of the constraint set.} of a large class of Euclidean norm (and more generally, group LASSO penalty) regularized convex optimization problems is a KL function with exponent $\frac12$. This complements the recent study in this direction \cite{LiPong18,YuLiPo19,YuLP20,ZYuP20}, and, in particular, gives rise to linear convergence of our method in solving these structured optimization models.
\end{itemize}

@@

\begin{theorem}[{{\bf Well-definedness of Algorithm~\ref{SQP_retract}}}]\label{welldef1}
Consider \eqref{P0} and suppose that Assumption~\ref{assumption1} holds. Suppose that $x^k\in {\cal F}$ is generated by the $k$-th iteration of Algorithm~\ref{SQP_retract} for some $k \ge 0$. Then the following statements hold:
\begin{enumerate}[{\rm (i)}]
   \item The convex subproblem \eqref{subproblem2} has a unique solution. Moreover, $\xfeas$ from Assumption~\ref{assumption1} is a Slater point of the feasible set of \eqref{subproblem2}, that is, $\xfeas\in C$ and $$\max\limits_{1 \le i \le m}\{g_i(x^k) + \langle \nabla g_i(x^k), \xfeas - x^k\rangle\} < 0.$$
   \item If $\max\limits_{1 \le i \le m} \{g_i(\widetilde{u})\} > 0$, then there exists $\widetilde{\tau}\in (0, 1)$ such that $\widetilde{x}:=(1 - \widetilde{\tau})\widetilde{u} + \widetilde{\tau} \xfeas$ satisfies $\max\limits_{1 \le i \le m} \{g_i(\widetilde{x})\} = 0$. Moreover, in this case, for any such $\widetilde\tau$, we have
       \begin{equation}\label{taubound0}
       \widetilde{\tau} \leq \frac{L\|\widetilde{u} - x^k\|^2}{-2\max\limits_{1 \le i \le m}\{g_i(\xfeas)\}}\ \ \ {and}\ \ \
       \|\widetilde{x} - \widetilde{u}\| \leq \frac{ML\|\widetilde{u} - x^k\|^2}{-2\max\limits_{1 \le i \le m}\{g_i(\xfeas)\}},
       \end{equation}
       where $M := \sup\limits_{x\in C}\|x - \xfeas\|$ and $L := \max\limits_{1 \le i \le m} L_{g_i}$, with $L_{g_i}$ being the Lipschitz continuity modulus of $\nabla g_i$ on $C$ for each $i$.
   \item Step 2 of algorithm \ref{SQP_retract} terminates in finitely many inner iterations.
 \end{enumerate}
 Thus, an $x^{k+1}\in {\cal F}$ can be generated at the end of the $(k+1)$-th iteration of Algorithm~\ref{SQP_retract}.
\end{theorem}
\begin{proof}
(i): First, we note that the feasible region of \eqref{subproblem2} is closed and convex. Next, we show that this set is nonempty by showing that it contains the point $\xfeas\in C$. Indeed, since each $g_i$ is convex, we have that for each $i$, $g_i(y) + \langle \nabla g_i(y),\xfeas - y\rangle\leq g_i(\xfeas) < 0$, for all $y\in \R^n$. This also shows that $\xfeas$ is a Slater point of the feasible set of \eqref{subproblem2}. Now, since $P_1$ is convex and continuous, we see that $x\mapsto P_1(x) - \langle \xi^k, x - x^k\rangle + \frac{1}{2\widetilde{\beta}}\|x - x^k\|^2$ is strongly convex and continuous for any $\widetilde{\beta} > 0$. Therefore, \eqref{subproblem2} is a convex optimization problem with a strongly convex objective function over a nonempty closed convex set, and hence, has a unique solution.

@@

\begin{theorem}[{{\bf Well-definedness of Algorithm~\ref{SQP_retract2}}}]\label{welldef2}
Consider \eqref{P1} and suppose that Assumptions~\ref{gassum} and \ref{assumption4} hold. Suppose that an $x^k\in {\cal F}_1$ is generated by the $k$-th iteration of Algorithm~\ref{SQP_retract2} for some $k\ge 0$. Then the following statements hold:
\begin{enumerate}[{\rm (i)}]
   \item The convex subproblem \eqref{subproblem4} has a unique solution. Moreover, $\xfeasss$ from Assumption~\ref{assumption4} is a Slater point of the feasible set of \eqref{subproblem4}.
   \item If $\ell^{x^k}(A\widetilde{u} - b) > \tilde{\sigma}^{x^k}$, then there exists $\widetilde{\tau}\in (0, 1)$ such that $\widetilde{x}:=(1 - \widetilde{\tau})\widetilde{u} + \widetilde{\tau} \xfeasss$ with $\ell^{x^k}(A\widetilde{x} - b) = \tilde{\sigma}^{x^k}$. Moreover, for any such $\widetilde\tau$, it holds that
       \[
       \widetilde{\tau} \leq \frac{L_{\ell}\|A\|^2}{2\sigmamin}\|\widetilde{u} - x^k\|^2
       \ \ {\it and}\ \ \|\widetilde{x} - \widetilde{u}\| \leq \frac{ML_{\ell}\|A\|^2}{2\sigmamin}\|\widetilde{u} - x^k\|^2,
       \]
       where $M := \sup\limits_{x\in C}\|x - \xfeasss\|$, and $\sigmamin$ and $L_\ell$ are defined as in Lemma~\ref{ell+}.
   \item Step 2 of algorithm \ref{SQP_retract2} terminates in finitely many inner iterations.
   \item For each $\widetilde{\beta} > 0$, the subproblem \eqref{subproblem4} has a Lagrange multiplier $\widetilde\lambda\geq 0$ and it satisfies
       \begin{equation*}
       0\in \partial P_1(\widetilde{u}) - \xi^k +\frac{1}{\widetilde{\beta}}(\widetilde{u} - x^k) +\widetilde\lambda A^T\nabla\ell(Ax^k - b) + \mathcal{N}_C(\widetilde{u}),
       \end{equation*}
       and
       \begin{equation*}
       \widetilde\lambda\big(\ell(Ax^k - b) + \langle A^T\nabla\ell(Ax^k - b), \widetilde{u}-x^k\rangle - \sigma\big) = 0.
       \end{equation*}
 \end{enumerate}
 In particular, an $x^{k+1}\in {\cal F}_1$ can be generated at the end of the $(k + 1)$-th iteration of Algorithm~\ref{SQP_retract2}.
\end{theorem}
\begin{proof}
(i): We first observe that the feasible region of \eqref{subproblem4} is  closed and convex. We next show that it is nonempty by showing that $\xfeasss$ is a Slater point of the feasible set of \eqref{subproblem4}.
To this end, we note from the convexity of $\ell^{x^k}$ (see Lemma~\ref{ell+}(ii)) that
\begin{equation}\label{relxxx}
\ell^{x^k}(Ax^k - b) + \langle A^T\nabla\ell^{x^k}(Ax^k - b), \xfeasss - x^k\rangle\leq\ell^{x^k}(A\xfeasss - b) \overset{\rm (a)}= \ell^{x^k}(0) \overset{\rm (b)}= 0 \overset{\rm (c)}< \tilde{\sigma}^{x^k},
\end{equation}
where (a) follows from Assumption~\ref{assumption4}, (b) follows from Lemma~\ref{ell+}(ii), and (c) holds because of Lemma~\ref{ell+}(i) and the fact that $x^k\in {\cal F}_1$. Hence,
\[
\begin{aligned}
  &\ell(Ax^k - b) + \langle A^T\nabla\ell(Ax^k - b), \xfeasss - x^k\rangle\\
  & = \sigma + \ell^{x^k}(Ax^k - b)- \tilde{\sigma}^{x^k} + \langle A^T\nabla\ell^{x^k}(Ax^k - b), \xfeasss - x^k\rangle < \sigma,
\end{aligned}
\]
where the equality follows from Lemma~\ref{ell+}(iv) and the inequality holds thanks to \eqref{relxxx}.
Since we also have $\xfeasss\in C$ by assumption, we have shown that $\xfeasss$ is a Slater point for \eqref{subproblem4}. Next, since $P_1$ is convex and continuous, it holds that $x\mapsto P_1(x) - \langle \xi^k, x - x^k\rangle + (2\widetilde{\beta})^{-1}\|x - x^k\|^2$ is strongly convex and continuous, for any $\widetilde{\beta} > 0$. Therefore, \eqref{subproblem4} has a unique solution.

@@

With these choices of $M > 0$, problem \eqref{E3} is a special case of \eqref{P0} with $m = 1$, $P_1(x)= \sum\limits_{J\in\mathcal{J}}\|x_J\|$, $P_2(x) = \mu\|x\|$, $g_1(x) = \|Ax - b\|^2 - \sigma^2$ and $C = \{x\in\R^n:\; \max\limits_{J\in \mathcal{J}}\|x_J\| \leq M\}$. Moreover, Assumption~\ref{assumption1} holds for \eqref{E3} with $\xfeas = \tx$. Therefore, we can apply Algorithm~\ref{SQP_retract} to \eqref{E3}. In our numerical experiments below, we will be solving random instances of \eqref{E3} with $M = (1 - \mu)^{-1}[\sum\limits_{J\in\mathcal{J}}\|\tx_J\| - \mu\|\tx\|]$.

>>>>

\section{Introduction}
We consider the following difference-of-convex (DC) optimization problem with smooth inequality and geometric constraints:
\begin{equation}\label{P0}
  \begin{array}{rl}
\min\limits_{x\in\R^n} & P(x) := P_1(x) - P_2(x)\\
{\rm s.t.} & g_i(x)\leq 0,~~ i = 1,\ldots, m,\\
           & x\in C,
  \end{array}
\end{equation}
where $P_1:\R^n\rightarrow\R$ and $P_2:\R^n\rightarrow\R$ are {\color{blue}finite-valued convex} functions, $C\subseteq \R^n$ is a nonempty compact convex set, $g_i:\R^n\rightarrow\R$ is smooth with Lipschitz gradient on $C$ for each $i$, and the feasible set $\mathcal{F} :=\{x\in C:\; g_i(x)\le 0, ~ i = 1,\ldots, m\}$ is nonempty.

The model problem (\ref{P0}) covers many important optimization problems arising from diverse areas. For example, one can model the compressed sensing (CS) problem with Cauchy noise by minimizing the difference of $\ell_1$-norm and $\ell_2$-norm \cite{YiLH15} or its variants subject to an inequality constraint defined by the so-called Lorentzian norm \cite{CaBA10}, and the set $C$ in \eqref{P0} can be used for modeling other prior information such as bounds or nonnegativity; more discussions on this particular application can be found in Section~\ref{sec6.2} below. Problem~\eqref{P0} is typically challenging to solve because it is in general nonconvex and nonsmooth.% optimization problem.

In this paper, we are interested in developing first-order feasible methods for solving problem \eqref{P0} that rely on affine approximations to the smooth inequality constraints in the subproblems. Our methods utilize only first-order information, and the subproblems that arise are convex constrained optimization problems with the constraint sets being the intersection of $C$ and a polyhedron. %\footnote{On passing, we would like to point out that there are also first-order methods that rely on quadratically approximating the constraint functions (see, for example, \cite{Au13,AuSheTeb10,BoPau16,YuLP20}), which lead to more difficult subproblems.}
 Moreover, it also has the desirable feature that  all the iterates generated always belong to the feasible region. In the literature, the most widely used method for solving \eqref{P0} when the objective function $P$ is additionally smooth and also involves affine approximations to the constraint set is the so-called sequential quadratic programming (SQP) method: Indeed, this class of methods typically further requires that the objective function $P$ and all the constraint functions $g_i$'s to be twice continuously differentiable. The underlying strategy of SQP methods is to construct an algorithm which, at each iteration, utilizes a convex quadratic programming problem with affine constraints to approximate the original nonlinear optimization problem. The literature is vast and we refer the readers to \cite{Ber95,NoWr06,GiWo12,FlGL02,So09,Au13,BoPau16,WrightTenny04,PaTi93,FlPa08,LawTits01}.
Recent works on SQP-type methods include \cite{Au13,BoPau16}, where the authors proposed and studied the global convergence of some general majorization minimization schemes which cover various SQP-type methods as special cases. However, these SQP-type methods therein are infeasible SQP-type methods, that is, they do not necessarily force all iterates to be feasible. There are also ``feasible SQP methods" that perform arc-search along quadratic curves determined by two directions, namely a descent direction and a feasible direction (see, for example, \cite{PaTi93,FlPa08,LawTits01}). However, these methods make use of the smoothness of the objective and constraint functions to construct the two directions, and it is unclear how their strategies can be adapted to problem~\eqref{P0} that has a possibly nonsmooth objective.

@@

{\color{blue} For nonconvex optimization problems with difference-of-convex structure, our method belongs to
the so-called successive convex programs strategy which, in each subproblem, a convex approximation to the constraint is formed. In the literature, popular methods of this form include the standard difference-of-convex algorithm (DCA) and its variants (see \cite{DCA18} for a recent survey), and also the moving balls approximation methods \cite{Au13,AuSheTeb10,BoPau16,YuLP20}. For these methods, their subproblems involve quadratic or general convex constraints which are, in general, harder to solve comparing to our proposed method because our method solves a linearly constrained problem in each subproblem.  It is also worth mentioning that the technique in using affine approximation for the constraints to construct numerical methods to solve possibly nonconvex problems has been exploited in the literature  (for example, see \cite{Veinott,AckOli16}). However, our method differs from these methods in various important aspects. More explicitly, \cite{Veinott,AckOli16} proposed the so-called supporting hyperplane methods which employ a cutting plane strategy. In particular, for the supporting hyperplane methods in \cite{Veinott,AckOli16}, as the algorithm progresses, the number of halfspaces involved in the subproblem {\em grows}, with many of them constructed based on information from the \emph{past iterates}. In contrast, our method only requires a {\it fixed} number of halfspaces in each iteration, and the constraint functions are linearized only at the \emph{current iterate}. Thus, the computational effort for solving each subproblem is similar in our method. In addition, due to the specific construction of the retraction step, our method ensures the descent property of the objective value: an important aspect that was not exploited in \cite{Veinott,AckOli16}.
%These type of methods   %including the recent studies on convergence to a stronger version of the stationarity \cite{PRA17}.
}

More explicitly, the contributions of this paper are summarized as follows:
\begin{itemize}
  \item We propose a retraction based first-order feasible method that utilizes affine approximations for the constraints in each subproblem for solving problem \eqref{P0} in the case where the constraint functions $g_i$'s are convex under strict feasibility condition, and establish its global subsequential convergence. We also analyze the convergence rate in the fully convex setting, i.e., when $P_2$ is also zero, under suitable Kurdyka-{\L}ojasiewicz (KL) assumptions.
  \item By assuming {\color{blue} a stronger version of the strict feasibility condition}, we then extend our method to solve \eqref{P0} with one single specially structured nonconvex constraint function and establish the global subsequential convergence of the extended method. Our assumptions on the constraint function are general enough to allow the choice of the composition of the Lorentzian norm function with an affine function, a commonly used loss function for compressed sensing problems with Cauchy measurement noise \cite{CaBA10}.
  \item Finally, we examine the KL exponents of several structured optimization models of the form \eqref{P0}, an important quantity which quantifies the convergence rate of the proposed method in the convex setting. Specifically, we show that the extended objective\footnote{This refers to the sum of the objective and the indicator function of the constraint set.} of a large class of Euclidean norm (and more generally, group LASSO penalty) regularized convex optimization problems is a KL function with exponent $\frac12$. This complements the recent study in this direction \cite{LiPong18,YuLiPo19,YuLP20,ZYuP20}, and, in particular, gives rise to linear convergence of our method in solving these structured optimization models.
\end{itemize}

@@

\begin{theorem}[{{\bf Well-definedness of Algorithm~\ref{SQP_retract}}}]\label{welldef1}
Consider \eqref{P0} and suppose that Assumption~\ref{assumption1} holds. Suppose that $x^k\in {\cal F}$ is {\color{blue} generated at the beginning of the $k$-th iteration} of Algorithm~\ref{SQP_retract} for some $k \ge 0$. Then the following statements hold:
\begin{enumerate}[{\rm (i)}]
   \item The convex subproblem \eqref{subproblem2} has a unique solution. Moreover, $\xfeas$ from Assumption~\ref{assumption1} is a Slater point of the feasible set of \eqref{subproblem2}, that is, $\xfeas\in C$ and $$\max\limits_{1 \le i \le m}\{g_i(x^k) + \langle \nabla g_i(x^k), \xfeas - x^k\rangle\} < 0.$$
   \item If $\max\limits_{1 \le i \le m} \{g_i(\widetilde{u})\} > 0$, then there exists $\widetilde{\tau}\in (0, 1)$ such that $\widetilde{x}:=(1 - \widetilde{\tau})\widetilde{u} + \widetilde{\tau} \xfeas$ satisfies $\max\limits_{1 \le i \le m} \{g_i(\widetilde{x})\} = 0$. Moreover, in this case, for any such $\widetilde\tau$, we have
       \begin{equation}\label{taubound0}
       \widetilde{\tau} \leq \frac{L\|\widetilde{u} - x^k\|^2}{-2\max\limits_{1 \le i \le m}\{g_i(\xfeas)\}}\ \ \ {and}\ \ \
       \|\widetilde{x} - \widetilde{u}\| \leq \frac{ML\|\widetilde{u} - x^k\|^2}{-2\max\limits_{1 \le i \le m}\{g_i(\xfeas)\}},
       \end{equation}
       where $M := \sup\limits_{x\in C}\|x - \xfeas\|$ and $L := \max\limits_{1 \le i \le m} L_{g_i}$, with $L_{g_i}$ being the Lipschitz continuity modulus of $\nabla g_i$ on $C$ for each $i$.
   \item Step 2 of algorithm \ref{SQP_retract} terminates in finitely many inner iterations.
 \end{enumerate}
 Thus, an $x^{k+1}\in {\cal F}$ can be generated at the end of the $(k+1)$-th iteration of Algorithm~\ref{SQP_retract}.
\end{theorem}
\begin{proof}
(i): First, we note that the feasible region of \eqref{subproblem2} is closed and convex. Next, we show that this set is nonempty by showing that it contains the point $\xfeas\in C$. Indeed, since each $g_i$ is convex, we have that for each $i$, $g_i(y) + \langle \nabla g_i(y),\xfeas - y\rangle\leq g_i(\xfeas) < 0$, for all $y\in \R^n$. This also shows that $\xfeas$ is a Slater point of the feasible set of \eqref{subproblem2}. Now, since $P_1$ is convex and continuous, we see that $x\mapsto P_1(x) - \langle \xi^k, x - x^k\rangle + \frac{1}{2\widetilde{\beta}}\|x - x^k\|^2$ is strongly convex and continuous for any $\widetilde{\beta} > 0$. Therefore, \eqref{subproblem2} is a convex optimization problem with a strongly convex objective function over a nonempty closed convex set, and hence, has a unique solution.

@@

\begin{theorem}[{{\bf Well-definedness of Algorithm~\ref{SQP_retract2}}}]\label{welldef2}
Consider \eqref{P1} and suppose that Assumptions~\ref{gassum} and \ref{assumption4} hold. Suppose that an $x^k\in {\cal F}_1$ is generated {\color{blue} at the beginning of the $k$-th iteration} of Algorithm~\ref{SQP_retract2} for some $k\ge 0$. Then the following statements hold:
\begin{enumerate}[{\rm (i)}]
   \item The convex subproblem \eqref{subproblem4} has a unique solution. Moreover, $\xfeasss$ from Assumption~\ref{assumption4} is a Slater point of the feasible set of \eqref{subproblem4}.
   \item If $\ell^{x^k}(A\widetilde{u} - b) > \tilde{\sigma}^{x^k}$, then there exists $\widetilde{\tau}\in (0, 1)$ such that $\widetilde{x}:=(1 - \widetilde{\tau})\widetilde{u} + \widetilde{\tau} \xfeasss$ with $\ell^{x^k}(A\widetilde{x} - b) = \tilde{\sigma}^{x^k}$. Moreover, for any such $\widetilde\tau$, it holds that
       \[
       \widetilde{\tau} \leq \frac{L_{\ell}\|A\|^2}{2\sigmamin}\|\widetilde{u} - x^k\|^2
       \ \ {\it and}\ \ \|\widetilde{x} - \widetilde{u}\| \leq \frac{ML_{\ell}\|A\|^2}{2\sigmamin}\|\widetilde{u} - x^k\|^2,
       \]
       where $M := \sup\limits_{x\in C}\|x - \xfeasss\|$, and $\sigmamin$ and $L_\ell$ are defined as in Lemma~\ref{ell+}.
   \item Step 2 of algorithm \ref{SQP_retract2} terminates in finitely many inner iterations.
   \item For each $\widetilde{\beta} > 0$, the subproblem \eqref{subproblem4} has a Lagrange multiplier $\widetilde\lambda\geq 0$ and it satisfies
       \begin{equation*}
       0\in \partial P_1(\widetilde{u}) - \xi^k +\frac{1}{\widetilde{\beta}}(\widetilde{u} - x^k) +\widetilde\lambda A^T\nabla\ell(Ax^k - b) + \mathcal{N}_C(\widetilde{u}),
       \end{equation*}
       and
       \begin{equation*}
       \widetilde\lambda\big(\ell(Ax^k - b) + \langle A^T\nabla\ell(Ax^k - b), \widetilde{u}-x^k\rangle - \sigma\big) = 0.
       \end{equation*}
 \end{enumerate}
 In particular, an $x^{k+1}\in {\cal F}_1$ can be generated at the end of the $(k + 1)$-th iteration of Algorithm~\ref{SQP_retract2}.
\end{theorem}
\begin{proof}
(i): We first observe that the feasible region of \eqref{subproblem4} is  closed and convex. We next show that it is nonempty by showing that $\xfeasss$ is a Slater point of the feasible set of \eqref{subproblem4}.
To this end, we note from the convexity of $\ell^{x^k}$ (see Lemma~\ref{ell+}(ii)) that
\begin{equation}\label{relxxx}
\ell^{x^k}(Ax^k - b) + \langle A^T\nabla\ell^{x^k}(Ax^k - b), \xfeasss - x^k\rangle\leq\ell^{x^k}(A\xfeasss - b) \overset{\rm (a)}= \ell^{x^k}(0) \overset{\rm (b)}= 0 \overset{\rm (c)}< \tilde{\sigma}^{x^k},
\end{equation}
where (a) follows from Assumption~\ref{assumption4}, (b) follows from Lemma~\ref{ell+}(ii), and (c) holds because of Lemma~\ref{ell+}(i) and the fact that $x^k\in {\cal F}_1$. Hence,
\[
\begin{aligned}
  &\ell(Ax^k - b) + \langle A^T\nabla\ell(Ax^k - b), \xfeasss - x^k\rangle\\
  & = \sigma + \ell^{x^k}(Ax^k - b)- \tilde{\sigma}^{x^k} + \langle A^T\nabla\ell^{x^k}(Ax^k - b), \xfeasss - x^k\rangle < \sigma,
\end{aligned}
\]
where the equality follows from Lemma~\ref{ell+}(iv) and the inequality holds thanks to \eqref{relxxx}.
Since we also have $\xfeasss\in C$ by assumption, we have shown that $\xfeasss$ is a Slater point for \eqref{subproblem4}. Next, since $P_1$ is convex and continuous, it holds that $x\mapsto P_1(x) - \langle \xi^k, x - x^k\rangle + (2\widetilde{\beta})^{-1}\|x - x^k\|^2$ is strongly convex and continuous, for any $\widetilde{\beta} > 0$. Therefore, \eqref{subproblem4} has a unique solution.

@@

With these choices of $M > 0$, problem \eqref{E3} is a special case of \eqref{P0} with $m = 1$, $P_1(x)= \sum\limits_{J\in\mathcal{J}}\|x_J\|$, $P_2(x) = \mu\|x\|$, $g_1(x) = \|Ax - b\|^2 - \sigma^2$ and $C = \{x\in\R^n:\; \max\limits_{J\in \mathcal{J}}\|x_J\| \leq M\}$. Moreover, Assumption~\ref{assumption1} holds for \eqref{E3} with $\xfeas = \tx$. Therefore, we can apply Algorithm~\ref{SQP_retract} to \eqref{E3}. In our numerical experiments below, we will be solving random instances of \eqref{E3} with $$M = (1 - \mu)^{-1}[\sum\limits_{J\in\mathcal{J}}\|\tx_J\| - \mu\|\tx\|].$$

\subsection{Compressed sensing with Cauchy noise for complex signals}\label{sec6.2}
{\color{blue} In compressed sensing for real signals, when the measurement (say, of dimension $2p$) is contaminated with Cauchy noise, the Lorentzian norm $\|y\|_{LL_2,\gamma}:= \sum\limits_{j=1}^{2p}\log(1 + \gamma^{-2}y_j^2)$ can be employed as the loss function \cite{CaBA10,CaRA16}, where $\gamma > 0$ and $y\in \R^{2p}$. Here we explore the scenario when the signal and the measurement matrix have \emph{complex} entries with the transmission contaminated by Cauchy noise. Specifically, in this setting, an unknown sparse vector ${\bf z}_0\in {\mathbb{C}}^n$ is compressed via multiplication with a given matrix ${\bf A}\in \mathbb{C}^{p\times n}$ and the resulting ${\bf A} {\bf z}_0$ is transmitted. The target is to recover approximately the vector ${\bf z}_0$ from the received signal ${\bf b} := {\bf A}{\bf z}_0 + \varepsilon$, where $\varepsilon \in {\mathbb{C}}^p$ is the noise vector, with the real and imaginary parts of each entry following an i.i.d. Cauchy distribution with mean $0$. In view of the structure of $\varepsilon$, we will view it as a random vector in $\R^{2p}$ with i.i.d. Cauchy entries and consider the Lorentzian norm for this real vector in our compressed sensing model below.
%As we will see soon, this will lead to an optimization model with group  loss function which takes the group lasso
